Your Title Here

### 2025-05-13 latex/draft.tex
更新论文

\section{Results}
This section presents the results

>>>>

\section{Results}
\subsection{Publication Volume}
 The analysis of annual publication counts reveals distinct patterns in research activity within this field. From 1997 to 2017, annual outputs remained below 20 publications, with initial stagnation (1 publication in 1997, fluctuating between 2–18 until 2017). A marked acceleration began in 2018, as publications surged from 42 to 450 by 2024, corresponding to a compound annual growth rate (CAGR) of 48\% over this six-year period. Annual growth rates varied significantly, peaking at 114\% between 2019–2020 (71→152 publications), followed by gradual moderation in percentage terms. Absolute annual increments exceeded 30 publications after 2020, reaching a maximum increase of 104 publications from 2023 to 2024 (346→450). These quantitative metrics demonstrate a sustained expansion of research engagement post-2018, with publication volume increasing 10.7-fold between 2018 and 2024.

\subsection{Keywords}
"A systematic analysis of keyword frequencies in drone logistics literature identifies three principal categories: (1) Platform terminology with drone (347) and unmanned aerial vehicle (316) as dominant descriptors, accompanied by operational concerns like energy consumption (23) and urban air mobility (24); (2) Navigation methodologies where routing (90) and path planning (57) form the core, supported by established optimization frameworks including vehicle routing problem (27) and traveling salesman problem (24); (3) Application contexts led by logistics (80) and drone delivery (79), with last-mile delivery (50) and parcel delivery (23) as specialized sub-themes. This keyword distribution pattern shows delivery applications exhibit fewer distinct high-frequency descriptors compared to platform technologies and navigation algorithms, where drone (347), unmanned aerial vehicle (316), routing (90), and their derivative terms form a denser lexical network.

\subsection{Authors}
Our analysis of highly cited authors in the drone logistics domain reveals ​​Jinsoo Hwang​​ from Sejong University as the most highly-cited scholar, with a total citation count of ​​1,434​​. Hwang’s research focuses on consumer behavior and technology adoption in drone food delivery services, with his seminal works addressing critical dimensions of service innovation (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and behavioral adoption (\cite{WOS:000605628800016}). Our analysis further identifies ​​Chase C. Murray​​ from Auburn University as the second most influential scholar in drone logistics, with a total citation count of ​​1,209​​. Murray’s research pioneers operational optimization in drone-assisted delivery systems, particularly through algorithmic innovations for truck-drone coordination, epitomized by his ​​seminal work​​ "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}). To our knowlege, it is ​​the first study to formalize the synchronized truck-drone routing problem as a novel variant of the vehicle routing problem (VRP). Stefan Poikonen from the University of Colorado Denver made contributions to drone logistics through his research on ​​vehicle routing problems with drones (VRPD)​​. His work set up theoretical frameworks for optimizing truck-drone coordination systems, introducing ​​worst-case analyses (\cite{WOS:000400384200003}) and ​​branch-and-bound algorithms (\cite{WOS:000468604000010}) to address operational challenges like synchronization and endurance constraints. ​​Seokcheon Lee​​ from Purdue University has advanced drone logistics through innovative models for ​​truck-drone coordinated delivery systems​​, focusing on scalability and real-world constraints. His work "Multiple traveling salesman problem with drones: Mathematical model and heuristic approach" (\cite{WOS:000460496000002}) introduced a ​​multi-truck-drone routing framework​​ using mixed-integer programming and heuristics to minimize delivery times. He further addressed ​​payload-energy dependency​​ and ​​No-Fly Zones​​ (\cite{WOS:000474324300017}), integrating battery life constraints and regulatory airspace restrictions. Kevin ​​Dorling, Jordan Heinrichs, Jordan Messier, and Sebastian Magierowski​​ advanced drone routing by developing ​​multi-trip VRPs​​ that optimize energy consumption models (payload/battery weight) and enable ​​drone reuse​​. Their work introduced ​​mixed-integer programs​​ and ​​simulated annealing heuristics​​, revealing inverse exponential cost-time tradeoffs and offering tools to balance delivery efficiency and budget constraints (\cite{WOS:000623397300001}). While individual contributions remain pivotal, several highly cited scholars in drone logistics have achieved prominence through ​​collaborative partnerships​​. For example, ​​Amanda G. Chu's citation impact stems largely from co-authoring ​​Chase C. Murray's foundational work on truck-drone routing optimization  (\cite{WOS:000353871700006}). Similarly, ​​Jinkyung Jenny Kim​​’s influential studies on consumer behavior in drone food delivery emerged from collaborations with ​​Jinsoo Hwang (\cite{WOS:000514800800001, WOS:000605628800016, WOS:000623397300001})​​, while ​​Bruce Golden​​’s theoretical advances in vehicle routing problems with drones were co-developed with ​​Stefan Poikonen(\cite{WOS:000400384200003, WOS:000468604000010})​​.
